Litrepl: Literate Paper Processor Promoting Transparency More Than Reproducibility

### 2024-12-28 paper/paper.tex
Update paper

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{svg}

@@

The operation of Litrepl is best illustrated through the following example:

\begin{verbatim}
$ cat input.tex
\begin{python}
print("Hello")
\end{python}
\begin{result}
\end{result}

$ cat input.tex | litrepl
\begin{python}
print("Hello")
\end{python}
\begin{result}
Hello
\end{result}
\end{verbatim}

In this example, the input document \verb|input.tex| contains a Python code
block that outputs the string "Hello". When the document is piped through
Litrepl, it processes the code block and inserts the result directly into the
document where specified.

>>>>

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{svg}
\usepackage{comment}

@@

The operation of Litrepl is best illustrated through the example below. Consider
the document named \verb|input.tex|:

\begin{comment}
\begin{sh}
echo '\begin{verbatim}'
echo '$ cat input.tex'
cat input.tex
echo '\end{verbatim}'
\end{sh}
\end{comment}
%lresult
\begin{verbatim}
$ cat input.tex
\begin{python}
import sys
print(f"Hello, {sys.platform}!")
\end{python}
\begin{result}
\end{result}
\end{verbatim}
%lnoresult

This document contains a Python code section and an empty result section marked
with the corresponding Latex environment tags. To "execute" the document we
pipe it though the Litrepl processor as follows:

\begin{comment}
\begin{sh}
echo '\begin{verbatim}'
echo '$ cat input.tex | litrepl'
echo "sys.platform='linux'" | litrepl repl python >/dev/null
cat input.tex | litrepl
echo '\end{verbatim}'
\end{sh}
\end{comment}
%lresult
\begin{verbatim}
$ cat input.tex | litrepl
\begin{python}
import sys
print(f"Hello, {sys.platform}!")
\end{python}
\begin{result}
Hello, linux!
\end{result}
\end{verbatim}
%lnoresult

Now we can see the expected greeting of the author's operating system platform.
The side-effect of this execution is the started session of the python
interpreter which is now running in the background. We can modify its state by
adding more section to the document and executing them selectively or e.g. by
accessing \verb|litrepl repl python| terminal. So for example, setting
\verb|sys.platform| to another value and re-evaluating the document would yield
a different greeting.
